### 2004-07-09 Documentation/Manual.tex
*** empty log message ***
GLoBES tour added

\usepackage{verbatim}
\usepackage{cite}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{a4wide}
\usepackage{fancyheadings}
\usepackage[footnotesize,bf]{caption}
\usepackage{makeidx}
\usepackage{ae,aecompl} % only for Type 1 fonts

@@

% Set as GLoBES command and add to index:
% Always use GLB when mentioning a command in text!
\newcommand{\GLB}[1]{{\tt #1} \index{{\tt #1}}}

@@

\begin{center}
{ \Large \bf
\GLOBES\ 1.X \\
General Long Baseline Experiment Simulator \\ }
\vspace*{0.5cm}
{\large \bf User's and reference manual }
\end{center}

@@

\GLOBES\ (``General Long Baseline Experiment Simulator'') is a flexible
software package to simulate neutrino long baseline experiments. On the
one hand, it contains a comprehensive abstract experiment definition
language, which allows to describe most classes of long baseline experinents
at an abstract level. On the other hand, it provides a C-library to 
process the experiment information in order to obtain oscillation
probabilities, rate vectors, and $\Delta \chi^2$-values. Currently, 
\GLOBES\ is available for Linux. Since the source code is included,
the modifications to other operating systems should be doable.

@@

With the C-library, one can extract the $\Delta \chi^2$ for all defined 
oscillation channels for an experiment or any combination of experiments.
Of course, also low-level information, such as oscillation
probabilities or event rates, can be obtained. \GLOBES\ includes the
simulation of neutrino oscillations in matter with arbitrary matter 
density profiles, as well as it allows to simulate the matter density
uncertainty. As one of the most
advanced features of \GLOBES , it provides the technology to 
project the $\Delta \chi^2$, which is a function of all oscillation
parameters, onto any subspace of parameters by local minimization. 
This approach allows the inclusion of multi-parameter-correlations,
where external input (\eg, from solar parameters) can be imposed, too.
Applications of the projection mechanism include the projections onto the $\stheta$-axis and the $\stheta$-$\deltacp$-plane. In addition, all oscillation parameters can be kept free to precicely localize 
degenerate solutions.

@@

The \GLOBES\ software may have two target groups: 
Physicists, who are mainly interested in optimizing the potential
of specific experimental setups, and others, who are mainly
interested in the physics potential of different experiment types
from a theoretical point of view.
For the first group, \AEDL\ could be the most interesting aspect of
\GLOBES , where the user interface is only a tool to obtain specific
parameter sensitivities. In this case, \GLOBES\ could, serve as a
unified tool for the comparison and optimization of different experiment
 setups on equal footing, where
it is the primary objective to simulate the experiments as accurate
as possible. In addition, changes in experimental parameters, such as
efficiences or the energy resolutions, can quickly be tested.
%
For the second user group, the pre-defined 
experiment definition files might already be sufficient to test
new conceptual approaches, and the user interface is the most interesting
aspect for sophisticated applications including correlations,
degeneracies, and multi-experiment setups. In either case, the \GLOBES\
software could serve as a platform for the exchange of experiment
definitions, and for an efficient splitting of work between
experimentalists and theorists.

The user interface functions are described in \Part~\ref{part:1} of 
this manual, which is the ``user's manual''. In there, first of all a 
short \GLOBES\ tour is given in \Chapt~\ref{chapter:tour} in order to 
have an overview over \GLOBES . 
After that, the user
interface is successively introduced from very basic to more sophisticated
function. Eventually, it is demonstrated how one can change many
experiment parameters at running time (such as baseline or target mass), and how one can ontain low-level
information. We recommend that everybody interested in \GLOBES\ should
become familiar at least with the concepts in \Chapt~\ref{chapter:tour}
 and some of the examples on the boxed pages. The examples can be 
 directly compiled 
 from the respective directory in the \GLOBES\ software package.

@@

Finally, \Part~\ref{part:3} of this manual serves as reference manual,
and the appendix contains further supplementary information.

@@

\input{part3}

>>>>

\usepackage{verbatim}
\usepackage{cite}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{a4wide}
\usepackage{fancyheadings}
\usepackage[footnotesize,bf]{caption}
\usepackage{makeidx}
\usepackage{ae,aecompl} % only for Type 1 fonts for readable pdf convert

@@

% Set as GLoBES command and add to index:
% Always use GLB when mentioning a command in text!
\newcommand{\GLB}[1]{{\tt #1}\index{{\tt #1}}}
% Always use GLBNS when adding a command to the index without showing it!
\newcommand{\GLBNS}[1]{\index{{\tt #1}}}
\newcommand{\gq}[1]{\begin{quote} {\tt #1} \end{quote}}
\newcommand{\go}[1]{$\rightarrow$ Output: \begin{quote} {\sf #1} \end{quote}}

@@

\begin{center}
{ \Large \bf
\GLOBES\ 1.X \\
General Long Baseline Experiment Simulator \\ }
\vspace*{0.5cm}
{\large \bf User's and reference manual }

\vspace*{1.5cm}
{\large \bf !!!DRAFT IN PROGRESS!!! }
\end{center}

@@

\GLOBES\ (``General Long Baseline Experiment Simulator'') is a flexible
software package to simulate neutrino long baseline experiments. On the
one hand, it contains a comprehensive abstract experiment definition
language, which allows to describe most classes of long baseline experiments
at an abstract level. On the other hand, it provides a C-library to 
process the experiment information in order to obtain oscillation
probabilities, rate vectors, and $\Delta \chi^2$-values. Currently, 
\GLOBES\ is available for Linux. Since the source code is included,
the modifications to other operating systems should be doable.

@@

With the C-library, one can extract the $\Delta \chi^2$ for all defined 
oscillation channels for an experiment or any combination of experiments.
Of course, also low-level information, such as oscillation
probabilities or event rates, can be obtained. \GLOBES\ includes the
simulation of neutrino oscillations in matter with arbitrary matter 
density profiles, as well as it allows to simulate the matter density
uncertainty. As one of the most
advanced features of \GLOBES , it provides the technology to 
project the $\Delta \chi^2$, which is a function of all oscillation
parameters, onto any subspace of parameters by local minimization. 
This approach allows the inclusion of multi-parameter-correlations,
where external input (\eg, from solar parameters) can be imposed, too.
Applications of the projection mechanism include the projections onto the $\stheta$-axis and the $\stheta$-$\deltacp$-plane. In addition, all oscillation parameters can be kept free to precisely localize 
degenerate solutions.

@@

The \GLOBES\ software may have two target groups: 
Physicists, who are mainly interested in optimizing the potential
of specific experimental setups, and others, who are mainly
interested in the physics potential of different experiment types
from a theoretical point of view.
For the first group, \AEDL\ could be the most interesting aspect of
\GLOBES , where the user interface is only a tool to obtain specific
parameter sensitivities. In this case, \GLOBES\ could, serve as a
unified tool for the comparison and optimization of different experiment
 setups on equal footing, where
it is the primary objective to simulate the experiments as accurate
as possible. In addition, changes in experimental parameters, such as
efficiencies or the energy resolutions, can quickly be tested.
%
For the second user group, the pre-defined 
experiment definition files might already be sufficient to test
new conceptual approaches, and the user interface is the most interesting
aspect for sophisticated applications including correlations,
degeneracies, and multi-experiment setups. In either case, the \GLOBES\
software could serve as a platform for the exchange of experiment
definitions, and for an efficient splitting of work between
experimentalists and theorists.

The user interface functions are described in \Part~\ref{part:1} of 
this manual, which is the ``user's manual''. In there, first of all a 
short \GLOBES\ tour is given in \Chapt~\ref{chapter:tour} in order to 
have an overview over \GLOBES . 
After that, the user
interface is successively introduced from very basic to more sophisticated
function. Eventually, it is demonstrated how one can change many
experiment parameters at running time (such as baseline or target mass), and how one can obtain low-level
information. We recommend that everybody interested in \GLOBES\ should
become familiar at least with the concepts in \Chapt~\ref{chapter:tour}
 and some of the examples on the boxed pages. The examples can be 
 directly compiled 
 from the respective directory in the \GLOBES\ software package.

@@

%Finally, \Part~\ref{part:3} of this manual serves as reference manual,
%and the appendix contains further supplementary information.

@@

% \input{part3}
